%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Predicting Go Moves Using Convolutional Neural Networks and the Caffe Framework} % Role
    {Ready, Set, Go!} % Title
    {UMBC Machine Learning Course} % Location
    {Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Directed Group Project, Designed Experiment and Network, Aggregated and Generated Dataset.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Large Integer Factoring for RSA Encryption on High Performance Cluster} % Role
    {RSA Public Key Factoring} % Title
    {UMBC Algorithms Course} % Location
    {Nov. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Gained Experience with High Performance Cluster and SLURM, Learned RSA encrtyption and associated number theroy.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {MEAN Stack Social Web-App for Food Delivery} % Role
    {Foodber!} % Title
    {UMBC Software Engineering Course} % Location
    {May 2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Worked on team developing full stack web application, Learned Javascript, Resolved Git conflicts.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Learning and Visualizing Go Using Structure vs Noise Classification} % Role
    {Ready, Set, Go! (part 2)} % Title
    {UMBC Computer Vision Course} % Location
    {May 2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Assembeled and Maintained Deep Learning System, Developed Methods to Visualize Network State and Learning.\newline Video Presentation Link: https://www.youtube.com/watch?v=-Yrwyu6z3V8 }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Survey of 4.3 Billion Cellular Automations for Edge of Chaos Complexity with multi-GPUs via OpenCL} % Role
    {Exhaustive Five-Neighboor Automata Survey} % Title
    {UMBC MAPLE AI Lab} % Location
    {July 2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Learned to use OpenCL and the AMDAPPSKD for large computational tasks. Found Edge of Chaos Cellular Automations.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
